\documentclass{article}
\usepackage{graphicx} % Required for inserting images

\title{Project OFS}
\author{Jonathan ter Haar (...) and Richard Wols (6919405)}
\date{April 2024}

\begin{document}

\maketitle

\section{Events}
\begin{itemize}
\item Car arriving
\item 
\end{itemize}

Pseudocode is the following
\begin{verbatim}
Event: Car_arriving(){
    schedule new Car_arriving()
}
Event: Car_leaving(){
}
\end{verbatim}

\section{Assumptions}
We make the following assumptions
\paragraph{Arriving cars}
\begin{itemize}
\item Cars arrive according to a Poisson process. 
\item If a car cannot find a spot to park, it will try an arbitrary other parking place, again according to the preferences in the table, excluding the parking spot it has tried.
\item The parking moment, the charging volume, and the moment of arrival are independent.
\item When a car arrives, but $1.4\cdot $charging\_time $<$  connection\_time, the connection time is changed until this is the case. The resulting distribution of connection times is not the same as the original distribution. We choose not to correct for this.
\end{itemize}
\paragraph{Solar panels}
\begin{itemize}
\item The generated amount of energy of a solar panel is independent of the amount of energy generated in previous hours on the same day.
\item During the period of an hour, the power output of the solar panels is constant
\item Pricing is independent of the power output of solar panels.
\item If solar energy is left over, it flows back into the external grid
\end{itemize}
\paragraph{Grid power}
\begin{itemize}
\item There is always enough grid power to provide the power at any time
\end{itemize}

\end{document}
